---
title: "Corona Virus Report"
author:
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: true
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(readr)

```


```{r, echo = FALSE, message = FALSE, warning = FALSE}
tut9dat <- read_csv("Data/Data_Tables_Criminal_Incidents_Visualisation_Year_Ending_December_2019.csv")
```




# Section 3

```{r filter-data-drug-offences, echo = FALSE, message = FALSE, warning = FALSE}
drug_offences <- tut9dat %>%
  filter(`Offence Division` == "C Drug offences")
```

```{r number-drug-off, echo = FALSE, message = FALSE, warning = FALSE}
number_drug_offences <- drug_offences %>%
  group_by(Year) %>%
  summarise(Number = n())
```

```{r number-drug-off-table, echo = FALSE, message = FALSE, warning = FALSE}
number_drug_offences %>%
  kable(caption = "Number of Drug Offences each Year") %>%
  kable_styling()
```

```{r graph-drug-offences, fig.cap="Number of Drug Offences each Year", echo = FALSE, message = FALSE, warning = FALSE}
ggplot(number_drug_offences,
       aes(x = Year,
       y = Number,
       group = Year)) +
  geom_col()
```

Table \@ref(tab:number-drug-off-table) summarises the number of drug offences each year, while Figure \@ref(fig:graph-drug-offences) presents the number of offences each year in a column chart. Both the table and the figure illustrate that the number of drug offences has remained consistent over time. 

# Citation examples


 @BC64 and this is another article about COVID @bai2020presumed and I can also cite R packages as follows @ggplot2






