---
title: "Corona Virus Report"
author:
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: true
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)

```


\clearpage

# Research questions:

- Visual summary of corona virus contagion and dead rates in  the following countries

  \begin{enumerate}
    \item Italia
    \item Germany
    \item Greece
    \item Switzerland 
    \item Sweden
    \item France
  \end{enumerate}
  
- Visual summary of corona virus cases and deaths rates in  the following countries

 \begin{enumerate}
   \item Italia
   \item Germany
 \end{enumerate}


# Data set introduction 

"The dataset contains the latest available public data on COVID-19 including a daily situation update, the epidemiological curve and the global geographical distribution (EU/EEA and the UK, worldwide).

On 12 February 2020, the novel coronavirus was named severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) while the disease associated with it is now referred to as COVID-19. Since the beginning of the coronavirus pandemic, ECDC’s Epidemic Intelligence team has been collecting on daily basis the number of COVID-19 cases and deaths, based on reports from health authorities worldwide. To insure the accuracy and reliability of the data, this process is being constantly refined. This helps to monitor and interpret the dynamics of the COVID-19 pandemic not only in the European Union (EU), the European Economic Area (EEA), but also worldwide. Every day between 6.00 and 10.00 CET, a team of epidemiologists screens up to 500 relevant sources to collect the latest figures. The data screening is followed by ECDC’s standard epidemic intelligence process for which every single data entry is validated and documented in an ECDC database. An extract of this database, complete with up-to-date figures and data visualisations, is then shared on the ECDC website, ensuring a maximum level of transparency." More information available \href{https://data.europa.eu/euodp/en/data/dataset/covid-19-coronavirus-data}{here}

# Exploratory data analysis

<!-- In Section \ref{section:data_intro} the data used in this report is described .... -->


```{r , echo = FALSE , message = FALSE, warning = FALSE}

# https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide

covid <- read_csv(file = "Data/worldwidecases.csv")

# head(covid)
# names(covid)
# str(covid)

```

## Overall

```{r covid-europe, echo = FALSE, fig.align = "center", fig.width = 6, fig.cap = "Rates of covid cases"}

covidrate_vis <- covid %>%
  mutate(date= as.Date(dateRep, format = "%d/%m/%y"),
         cases_rates = ((1000*cases/popData2018) + 0.01),
         dead_rates = ((1000*deaths/popData2018) +0.01)) %>%
  dplyr::filter(date != "2020-12-31") %>%
  #group_by(countriesAndTerritories, date) %>%
  #summarize_at(vars(cases, deaths), cumsum) %>%
  dplyr::filter(countriesAndTerritories %in% c("Italy", "Germany", "Greece", "Switzerland", "Sweden", "France")) %>%
  ggplot(aes(x = date, y = cases_rates) ) +
  geom_line(color = "#1F9E8E")  +
  facet_wrap(~countriesAndTerritories) +
  theme_bw() +
  ggtitle("Covid cases (rates")
covidrate_vis
```


In figure \@ref(fig:covid-europe) we observe the corona virus rates of a number of european countries ...

```{r coviddeath1, echo = FALSE, fig.align = "center", fig.width = 6, fig.cap = "Death reates for COVID19"}

dead_rates_vis <- covid %>%
  mutate(date= as.Date(dateRep, format = "%d/%m/%y"),
         cases_rates = ((1000*cases/popData2018) + 0.01),
         dead_rates = ((1000*deaths/popData2018) +0.01)) %>%
  dplyr::filter(date != "2020-12-31") %>%
  #group_by(countriesAndTerritories, date) %>%
  #summarize_at(vars(cases, deaths), cumsum) %>%
  dplyr::filter(countriesAndTerritories %in% c("Italy", "Germany", "Greece", "Russia", "Sweden", "France")) %>%
  ggplot(aes(x = date, y = dead_rates) ) +
  geom_line(color = "#482878")  +
  facet_wrap(~countriesAndTerritories) +
  theme_bw() +
  ggtitle("Covid death cases (rates)")

dead_rates_vis

```

Figure \@ref(fig:coviddeath1) wdisplay the death reates of corona virus rates in Italy, Germany ...

\clearpage

## Oceania

```{r oceania-cases, echo = FALSE, fig.align = "center", fig.width = 6, fig.cap = "COVID cases in Australia and New Zealand"}

covidrate_vis <- covid %>%
  mutate(date= as.Date(dateRep, format = "%d/%m/%y"),
         cases_rates = ((1000*cases/popData2018) + 0.01),
         dead_rates = ((1000*deaths/popData2018) +0.01)) %>%
  dplyr::filter(date != "2020-12-31") %>%
  #group_by(countriesAndTerritories, date) %>%
  #summarize_at(vars(cases, deaths), cumsum) %>%
  dplyr::filter(countriesAndTerritories %in% c("Australia", "New_Zealand")) %>%
  ggplot(aes(x = date, y = cases_rates) ) +
  geom_line(color = "#1F9E8E")  +
  facet_wrap(~countriesAndTerritories) +
  theme_bw() +
  ggtitle("Covid cases (rates")
covidrate_vis
```

The rates of corona virus in Australia and New Zealand over time are displayed in \@ref(fig:oceania-cases)


```{r oceania-death, echo = FALSE, fig.align = "center", fig.width = 6, fig.cap = "Death rates of COVID in Oceania"}

dead_rates_vis <- covid %>%
  mutate(date= as.Date(dateRep, format = "%d/%m/%y"),
         cases_rates = ((1000*cases/popData2018) + 0.01),
         dead_rates = ((1000*deaths/popData2018) +0.01)) %>%
  dplyr::filter(date != "2020-12-31") %>%
  #group_by(countriesAndTerritories, date) %>%
  #summarize_at(vars(cases, deaths), cumsum) %>%
  dplyr::filter(countriesAndTerritories %in% c("Australia", "New_Zealand")) %>%
  ggplot(aes(x = date, y = dead_rates) ) +
  geom_line(color = "#482878")  +
  facet_wrap(~countriesAndTerritories) +
  theme_bw() +
  scale_fill_viridis_d() +
  ggtitle("Covid death cases (rates)")

dead_rates_vis

```

The death rates of corona virus in Australia and New Zealand over time are displayed in \@ref(fig:oceania-death)


# Comparisons


```{r , echo = FALSE, fig.align = "center", fig.width = 6}

monthly_comp <- covid %>%
  mutate(date= as.Date(dateRep, format = "%d/%m/%y")) %>%
  dplyr::filter(date != "2020-12-31") %>%
  dplyr::filter(countriesAndTerritories %in% c("Australia", "New_Zealand")) %>%
  group_by(countriesAndTerritories, month, year) %>%
  summarize_at(vars(cases, deaths), list(mean), na.rm = TRUE)

  ggplot(monthly_comp , aes(x = month, y = cases, fill = countriesAndTerritories) ) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_viridis_d() +
  theme_bw() +
  ggtitle("Covid death cases (rates)")



```


```{r , echo = FALSE, fig.align = "center", fig.width = 6, fig.cap = "Covid cases"}

monthly_comp_all <- covid %>%
  mutate(date= as.Date(dateRep, format = "%d/%m/%y")) %>%
  dplyr::filter(date != "2020-12-31") %>%
  dplyr::filter(countriesAndTerritories %in% c("Australia", "New_Zealand","Italy", "Germany", "Greece", "Russia", "Sweden", "France")) %>%
  group_by(countriesAndTerritories, month, year) %>%
  summarize_at(vars(cases, deaths), list(sum), na.rm = TRUE)

  ggplot(monthly_comp_all , aes(x = month, y = cases, fill = countriesAndTerritories) ) +
  geom_bar(stat="identity", position=position_dodge()) +
  theme_bw() +
  scale_fill_viridis_d(direction = -1) +
  ggtitle("Covid death cases (rates)")

```

\clearpage

```{r covidtab, echo = FALSE}
kable(monthly_comp_all, "latex", caption = "Covid cases and deaths per month", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))
```

In Table \@ref(tab:covidtab).

\clearpage

# Citation examples


 @BC64 and this is another article about COVID @bai2020presumed and I can also cite R packages as follows @ggplot2






